## Lab 1: An Introduction to Programming in R

### Lauren Wu

This assignment is due at 6:00 PM CST the day of lab. Please provide answers in <span style="color:blue"> blue text </span> and code in code chunks. Knit this file when you are done to check that all code runs. Remember to rename the file to contain *your actual* Last and First name and **submit both the Rmd and Html file to the submission link on Canvas**.


**3.1** 
```{r}
pi^11
```


**3.2**
```{r}
pi * 4e9
```


**3.3**
```{r}

```
<span style="color:blue"> 
The console returns as an error message. This is because R interpreted 4(2+3) as an attempt to call a function 4(), which doesn't exist.
\span


**4.1**
```{r}
TRUE + TRUE
```
<span style="color:blue"> 
R assigns a numerical value of 1 to TRUE and 0 to FALSE.
\span


**4.2**
```{r}
movie <- "Everything Everywhere All At Once"
```


**5.1**
<span style="color:blue"> 
!= assesses whether two things are not equal. 
>= assesses whether the left is larger than or equal to the right.
<= assesses whether the left is smaller than or equal to the right.
< assesses whether the left is smaller than the right. 
> assesses whether the left is larger than the right
\span

**5.2**
<span style="color:blue"> 
|| represents the OR operator. If any one of the statements are TRUE, the expression will return TRUE.
\span


**5.3**
```{r}
x <- 5
(x > 6) || (x < 8)
(x > 6) || (x > 8)
```


**6.1**
```{r}
carSpeed <- 35
speedLimit <- 30
if(carSpeed > speedLimit){ 
    print("Give ticket") 
}else{ 
    print("Do nothing") 
}
```
<span style="color:blue"> 
when carSpeed <- 35, it fulfills the condition for the code in "if", which executes print("Give ticket").
when carSpeed <- 29, it doesn't fulfill the condition for the code in if, which leads the code to execute "else", printing "Do nothing".
\span


**6.2**
```{r}
patientTemperature <- 103
if(patientTemperature < 95 || patientTemperature > 103){
  print("seek medical attention")
}else{
  print("do nothing")
}
```


**6.3**
```{r}
if(0){
  print("a")
}else {
  print("b")
}
```
<span style="color:blue"> 
R reads 0 as false. Because the if condition is false, a is not printed. Because the condition for else is not false, b is printed.
\span


**6.4**
```{r}
person <- "happy"
weather <- "raining"
if(person == "happy"){
  if(weather == "sunny"){
    print("Go outside")
  }else {
    print("Stay inside :(")
  }
}else{
  print("Stay inside")
}
```


**7.1**
```{r}
for(i in 1:3){
    x <- i + 10
    y <- x * 2
    z <- y ^ 2    
    print(z)
}
```
<span style="color:blue"> 
i is a variable that R substitutes values from 1 to 3 to execute the for loop. x, y, z, and i are all global variables. Defining variables i and z outside the loop prior to its execution will not affect its execution.
\span


**7.2**
```{r}
for(i in letters){
  UPPER <- toupper(i)
  print(UPPER)
}
```

**7.3**
<span style="color:blue"> 
when x is even, the value of x%%y is 0. When x is odd, the value is 1.
\span

```{r}
y <- 2
for(x in 1:15){
  q <- x%%y
  if(q == 1 || x == 12){
    print(x)}
}
```


**7.4**
<span style="color:blue"> 
This loop would continue to execute infinitely because x would always be larger than 0, so the condition to execute the while loop is always fulfilled.
\span
```{r}
#     ^take out eval = F hen you're done before knitting the file

x <- 10
while(x > 0){
    print(x)
    x <- x - 1
}
```

